---
title: "P8105 hmoework 3"
author: "Shunyi Zhang"
output: github_document
editor_options: 
  chunk_output_type: console
---

This is my solution for homework 3.

```{r setup, include=FALSE}
library(tidyverse)
library(p8105.datasets)

knitr::opts_chunk$set(
	fig.width = 6, 
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))

```

# Problem 1 

## Get data
```{r}
data("instacart")
```

## Explore data
The dimension of this data is `r dim(instacart)`. It has `r nrow(instacart)` rows and `r ncol(instacart)` columns. It contains variables `r ls(instacart)`. 

It has variable for user `user_id`. Variables for orders are `order_id`, `order_dow`, and `order_hour_of_day`. Variables for products are `product_id` and `product_name`. There are also variables about aisle and department, `aisle`, `aisle_id`, `department`, and `department_id`.

## Explore aisle
```{r}
instacart %>% 
  count(aisle) %>% 
  arrange(desc(n))
```
There are 134 aisles. Among them, the aisle of fresh vegetables is the most items ordered from.




